### 2021-10-22 paper/pldi22/formal.tex
More formalization in appendix

We first define $\ires$ as a specification language to describe JavaScript
semantics.  Then, we define a function specialization in $\ires$ with two
different source-to-source transformations: a constant propagation
transformation and a redundancy elimination transformation.  We prove the
semantics preservation of function specialization under an observational
semantics.  Finally, we define the JavaScript semantics specialization with
syntactic views using function specialization.

@@

A source-to-source transformation is defined with parameteric restrictions
$\restrictset$ and its concretization $\gamma: \restrictset \rightarrow
\powerset{\stset \times \valset^*}$.
\[
  \framebox{$\transf: \funcset \times \restrictset \rightarrow \funcset$}
\]

@@

\subsubsection{Constant Propagation Transformation}
\[
  \begin{array}{lr@{~}c@{~}l}
    \text{Restrictions} & (\valoptset)^* &=& (\valset \uplus \{ \top \})^*\\
    \text{Concretization} & \gamma(\valopt_1, \cdots, \valopt_n) &=& \\
    \multicolumn{4}{l}{\qquad \{
      (\st, (\val_1, \cdots, \val_n)) \mid
      \val_i \in \left\{
        \begin{array}{ll}
          \valset & \text{if} \; \valopt_i = \top\\
          \{ \valopt_i \} & \text{otherwise}\\
        \end{array}
      \right.
    \}}\\
  \end{array}
\]

In the constant propagation transformation, restrictions $(\valoptset)^*$ are
sequences of static values $\valset$ or a dynamic value $\top$.

\[
  \framebox{$\transcpe: \exprset \times \envset \rightarrow \exprset$}
\]

@@

\[
  \framebox{$\transcpi: \instset \times \envset \rightarrow \instset \times
  \envset$}
\]

@@

\[
  \framebox{$\transcpf: \funcset \times (\valoptset)^* \rightarrow \funcset$}
\]

\subsubsection{Redundancy Elimination Transformation}

\[
  \begin{array}{lr@{~}c@{~}l}
    \text{Restrictions} &\{ \top \}\\
    \text{Concretization} & \gamma(\top) &=& \stset \times \valset^*\\
  \end{array}
\]

The redundancy elimination transformation is defined without any restriction,
which means its restriction set consists of a single element $\top$
representing all possible cases.  Therefore, we omit the restriction part in
this transformation for the brevity.

\[
  \framebox{$\transref: \funcset \rightarrow \funcset$}
\]

>>>>

We first define $\ires$ as a specification language to describe JavaScript
semantics.  Then, we introduce a general formalization of function
specialization in $\ires$. Finally, we define a constant propagation
specialization as its an instance to reduce JavaScript semantics using given
syntactic views. We also prove its semantics preservation under an observational
semantics.

@@

A function specialization is defined with the following three components:
\begin{itemize}
  \item Restriction $\restrictset$
  \item Concretization $\gamma: \restrictset \rightarrow \powerset{\stset
    \times \valset^*}$
  \item Transformation $\trans: \restrictset \rightarrow \funcset \rightarrow
    \funcset$.
\end{itemize}

@@

\subsubsection{Constant Propagation Specialization}
\begin{itemize}
  \item Restriction $\cprestrictset = (\valoptset)^* =
    (\valset \uplus \{ \top \})^*$
  \item Concretization $\cpgamma: (\valoptset)^* \rightarrow \powerset{\stset
    \times \valset^*}$ s.t.
    \[
      \cpgamma(\valopt_1, \cdots, \valopt_n) = \stset \times (V_1 \times \cdots
      \times V_n)
    \]
    where $V_i = \left\{
      \begin{array}{ll}
        \valset & \text{if} \; \valopt_i = \top\\
        \{ \valopt_i \} & \text{otherwise}\\
      \end{array}
    \right.$
  \item Transformation $\cptrans: (\valoptset)^* \rightarrow \funcset
    \rightarrow \funcset$
\end{itemize}
In the constant propagation specialization, a restriction is a sequences of
static values $\valset$ or a dynamic value $\top$.

\[
  \begin{array}{lr@{~}c@{~}l@{~}c@{~}l}
    \text{Symbolic Environments} & \senv &\in& \senvset &=&
    \varset \finmap \svalset\\
    \text{Symbolic Values} & \sval &\in& \svalset &=&
    \valoptset \times \exprset\\
  \end{array}
\]

\[
  \framebox{$\cptranse: \exprset \times \senvset \rightarrow \svalset$}
\]

\[
  \begin{array}{lcl}
    \cptranse(\pval, \env) &=& \pval\\
    \cptranse(\op \kwrl \expr^* \kwrr, \env) &=& \todo\\
    \cptranse(\kwcl \kwcr, \env) &=& \todo\\
    \cptranse(\refer, \env) &=& \todo\\
  \end{array}
\]

\[
  \framebox{$\cptransi: \instset \times \senvset \rightarrow \instset \times
  \senvset$}
\]

@@

\[
  \framebox{$\cptrans: (\valoptset)^* \rightarrow \funcset \rightarrow
  \funcset$}
\]

@@

% \subsubsection{Redundancy Elimination Transformation}
% 
% \[
%   \begin{array}{lr@{~}c@{~}l}
%     \text{Restrictions} &\{ \top \}\\
%     \text{Concretization} & \gamma(\top) &=& \stset \times \valset^*\\
%   \end{array}
% \]
% 
% The redundancy elimination transformation is defined without any restriction,
% which means its restriction set consists of a single element $\top$
% representing all possible cases.  Therefore, we omit the restriction part in
% this transformation for the brevity.
% 
% \[
%   \framebox{$\transref: \funcset \rightarrow \funcset$}
% \]
% 
% \todo
